Multi-Robot Probabilistic Mapping and Exploration

### 2018-07-02 Dissertation/Thesis/tex/ae2D.tex
added and edited Secion 6.1
added & edited sec. 7.1 (Pioneer ground experiment)
figure captions in chap 3 updated

\begin{figure}
	\centering
    	\begin{subfigure}[b]{0.45\textwidth}
        		\includegraphics[width=\textwidth]{JustifyApprox_eH.pdf}
        		\caption{Entropy Error}
        		\label{fig:H_err}
    	\end{subfigure}
	\begin{subfigure}[b]{0.45\textwidth}
        		\includegraphics[width=\textwidth]{JustifyApprox_t.pdf}
        		\caption{Computation Ratio}
        		\label{fig:H_comp_ratio}
    	\end{subfigure}
\caption{The entropy error is decreased at the cost of increasing computation time in this Monte Carlo 1D measurement ray expected entropy case.}
\label{fig:ApproxJust}
\end{figure}

@@

\begin{figure}
\vspace*{0.1\columnwidth}
\centerline{
	\includegraphics[height=0.35\columnwidth]{ExampleOptimalPose.png}
}
\begin{picture}(0,0)(0,0)
\setlength{\unitlength}{0.1\columnwidth}\scriptsize
\put(4.4,2.1){\color{blue}$X_t$}
\put(5.9,1.9){\color{red}$x_1$}
\put(2.9,2.0){\color{red}$x_5$}
\put(4.4,3.6){\color{red}$x_3$}
\put(4.4,0.6){\color{red}$x_7$}
\put(5.4,3.0){\color{red}$x_2$}
\put(3.3,3.1){\color{red}$x_4$}
\put(3.3,1.0){\color{red}$x_6$}
\put(5.4,1.0){\color{red}$x_8$}
\put(6.8,3.1){\color{red}$z_{2,1}$}
\put(4.5,3.1){\color{red}$z_{2,5}$}
\put(5.6,4.1){\color{red}$z_{2,3}$}
\put(5.6,2.2){\color{red}$z_{2,7}$}
\put(6.5,3.7){\color{red}$z_{2,2}$}
\put(4.9,3.8){\color{red}$z_{2,4}$}
\put(5.0,2.5){\color{red}$z_{2,6}$}
\put(6.5,2.5){\color{red}$z_{2,8}$}
\put(6.1,2.9){$X_c^*$}
\end{picture}
\caption{This figure illustrates the expanding ring method. Initially, a robot (blue circle) views down and left (blue sector). Then, the robot considers $n_c=8$ poses (red circles) as possible candidates for where to move next. For each candidate, $n_d=8$ directions are considered (red lines, only displayed on candidate location $c=2$). Then, the expected entropy of each ray is calculated. The scan (red sector) covering those rays with the largest expected entropy decrease is chosen for each candidate, and the best candidate $X_c^*$ (black circle: location, black sector: scan) is chosen to maximize information gain. Finally, Dijkstra's algorithm provides the collision-free motion between $X_t$ and $X_c^*$, and the process is repeated.
}
\label{fig:OptProcess}
\end{figure}

@@

There are two important steps to moving a robot on a collision-free trajectory to its optimal pose. First, Dijkstra's algorithm provides the cost map and optimal collision-free waypoints. Then, a constrained polynomial least squares trajectory serves as the desired path, which is followed by a controller.

@@

\section{Numerical Examples}

@@

\begin{figure}
\centering{
    	\begin{subfigure}[b]{0.3\textwidth}
        		\includegraphics[width=\textwidth]{CDC16_t50.png}
        		\caption{Map at $t=50$ sec}
%        		\label{fig:}
    	\end{subfigure}
	\hspace*{0.01\columnwidth}
	\begin{subfigure}[b]{0.3\textwidth}
        		\includegraphics[width=\textwidth]{CDC16_t100.png}
        		\caption{Map at $t=100$ sec}
%        		\label{fig:}
    	\end{subfigure}
	\hspace*{0.01\columnwidth}
	\begin{subfigure}[b]{0.3\textwidth}
        		\includegraphics[width=\textwidth]{CDC16_t150.png}
        		\caption{Map at $t=150$ sec}
%        		\label{fig:}
    	\end{subfigure}
}
\centering{
    	\begin{subfigure}[b]{0.3\textwidth}
        		\includegraphics[width=\textwidth]{CDC16_t200.png}
        		\caption{Map at $t=100$ sec}
%        		\label{fig:}
    	\end{subfigure}
	\hspace*{0.01\columnwidth}
	\begin{subfigure}[b]{0.3\textwidth}
        		\includegraphics[width=\textwidth]{CDC16_t250.png}
        		\caption{Map at $t=250$ sec}
%        		\label{fig:}
    	\end{subfigure}
	\hspace*{0.01\columnwidth}
	\begin{subfigure}[b]{0.3\textwidth}
        		\includegraphics[width=\textwidth]{CDC16_t300.png}
        		\caption{Map at $t=300$ sec}
%        		\label{fig:}
    	\end{subfigure}
}
\centering{
    	\begin{subfigure}[b]{0.3\textwidth}
        		\includegraphics[width=\textwidth]{CDC16_t350.png}
        		\caption{Map at $t=350$ sec}
%        		\label{fig:}
    	\end{subfigure}
	\hspace*{0.01\columnwidth}
	\begin{subfigure}[b]{0.3\textwidth}
        		\includegraphics[width=\textwidth]{CDC16_t400.png}
        		\caption{Map at $t=400$ sec}
%        		\label{fig:}
    	\end{subfigure}
	\hspace*{0.01\columnwidth}
	\begin{subfigure}[b]{0.3\textwidth}
        		\includegraphics[width=\textwidth]{CDC16_t450.png}
        		\caption{Map at $t=450$ sec}
%        		\label{fig:}
    	\end{subfigure}
}
\caption{A robot (green circle, green marker of previous path) measures a room with a Kinect depth sensor to maximize map information gain.}
\label{fig:AutonomousExploration}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{intel_clean.png}
    \caption{Intel Research Lab floor plan benchmark~\cite{kummerle2009measuring}.}
\label{fig:intel}
\end{figure}

\begin{figure}[!ht]
    \centering
    \begin{subfigure}[t]{0.3\columnwidth}
        \centering
        \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{0min.png}
        \caption{$t=0$ min}
        \label{fig:IRL0min}
    \end{subfigure}
    \begin{subfigure}[t]{0.3\columnwidth}
        \centering
        \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{5min.png}
        \caption{$t=5$ min}
        \label{fig:IRL5min}
    \end{subfigure}
    \begin{subfigure}[t]{0.3\columnwidth}
           \centering
           \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{10min.png}
        \caption{$t=10$ min}
        \label{fig:IRL10min}
    \end{subfigure}
    \begin{subfigure}[t]{0.3\columnwidth}
           \centering
           \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{15min.png}
        \caption{$t=15$ min}
        \label{fig:IRL15min}
    \end{subfigure}
    \begin{subfigure}[t]{0.3\columnwidth}
         \centering
         \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{20min.png}
        \caption{$t=20$ min}
        \label{fig:IRL20min}
    \end{subfigure}
    \begin{subfigure}[t]{0.3\columnwidth}
           \centering
           \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{25min.png}
        \caption{$t=25$ min}
        \label{fig:IRL25min}
    \end{subfigure}
    \begin{subfigure}[t]{0.3\columnwidth}
           \centering
           \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{30min.png}
        \caption{$t=30$ min}
        \label{fig:IRL30min}
    \end{subfigure}
    \begin{subfigure}[t]{0.3\columnwidth}
           \centering
           \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{35min.png}
        \caption{$t=35$ min}
        \label{fig:IRL35min}
    \end{subfigure}
    \begin{subfigure}[t]{0.3\columnwidth}
           \centering
           \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{40min.png}
        \caption{$t=40$ min}
        \label{fig:IRL40min}
    \end{subfigure}
    \caption{A robot (green) measures a room in the ROS Stage simulator using the Intel Research Lab floor plan. The exact inverse sensor model is used for the autonomous exploration algorithm.}
    \label{fig:IRL}
\end{figure}

>>>>

\begin{figure}
	\centering
    	\begin{subfigure}[b]{0.45\textwidth}
        		\includegraphics[width=\textwidth]{JustifyApprox_eH.pdf}
        		\caption{Entropy Error}
        		\label{fig:H_err}
    	\end{subfigure}
	\begin{subfigure}[b]{0.45\textwidth}
        		\includegraphics[width=\textwidth]{JustifyApprox_t.pdf}
        		\caption{Computation Ratio}
        		\label{fig:H_comp_ratio}
    	\end{subfigure}
	\caption{Expected Entropy Computational Improvement of Reduced Ray Cells Considered}
	\medskip
	\small
	The entropy error is decreased at the cost of increasing computation time in this Monte Carlo 1D measurement ray expected entropy case.
	\label{fig:ApproxJust}
\end{figure}

@@

\begin{figure}
\vspace*{0.1\columnwidth}
\centerline{
	\includegraphics[height=0.35\columnwidth]{ExampleOptimalPose.png}
}
\begin{picture}(0,0)(0,0)
\setlength{\unitlength}{0.1\columnwidth}\scriptsize
\put(4.4,2.1){\color{blue}$X_t$}
\put(5.9,1.9){\color{red}$x_1$}
\put(2.9,2.0){\color{red}$x_5$}
\put(4.4,3.6){\color{red}$x_3$}
\put(4.4,0.6){\color{red}$x_7$}
\put(5.4,3.0){\color{red}$x_2$}
\put(3.3,3.1){\color{red}$x_4$}
\put(3.3,1.0){\color{red}$x_6$}
\put(5.4,1.0){\color{red}$x_8$}
\put(6.8,3.1){\color{red}$z_{2,1}$}
\put(4.5,3.1){\color{red}$z_{2,5}$}
\put(5.6,4.1){\color{red}$z_{2,3}$}
\put(5.6,2.2){\color{red}$z_{2,7}$}
\put(6.5,3.7){\color{red}$z_{2,2}$}
\put(4.9,3.8){\color{red}$z_{2,4}$}
\put(5.0,2.5){\color{red}$z_{2,6}$}
\put(6.5,2.5){\color{red}$z_{2,8}$}
\put(6.1,2.9){$X_c^*$}
\end{picture}
\caption{Optimal Pose Selection Illustration
}
	\medskip
	\small
	This figure illustrates the expanding ring method. Initially, a robot (blue circle) views down and left (blue sector). Then, the robot considers $n_c=8$ poses (red circles) as possible candidates for where to move next. For each candidate, $n_d=8$ directions are considered (red lines, only displayed on candidate location $c=2$). Then, the expected entropy of each ray is calculated. The scan (red sector) covering those rays with the largest expected entropy decrease is chosen for each candidate, and the best candidate $X_c^*$ (black circle: location, black sector: scan) is chosen to maximize information gain. Finally, Dijkstra's algorithm provides the collision-free motion between $X_t$ and $X_c^*$, and the process is repeated.
\label{fig:OptProcess}
\end{figure}

@@

There are two important steps to moving a robot on a collision-free trajectory to its optimal pose. First, Dijkstra's algorithm~\cite{Dij59} provides the cost map and optimal collision-free waypoints. Then, a constrained polynomial least squares trajectory serves as the desired path, which is followed by a controller.

@@

\section{Numerical Examples}
\label{sec:Ae2DNumExamples}

@@

\begin{figure}
\centering{
    	\begin{subfigure}[b]{0.3\textwidth}
        		\includegraphics[width=\textwidth]{CDC16_t50.png}
        		\caption{Map at $t=50$ sec}
%        		\label{fig:}
    	\end{subfigure}
	\hspace*{0.01\columnwidth}
	\begin{subfigure}[b]{0.3\textwidth}
        		\includegraphics[width=\textwidth]{CDC16_t100.png}
        		\caption{Map at $t=100$ sec}
%        		\label{fig:}
    	\end{subfigure}
	\hspace*{0.01\columnwidth}
	\begin{subfigure}[b]{0.3\textwidth}
        		\includegraphics[width=\textwidth]{CDC16_t150.png}
        		\caption{Map at $t=150$ sec}
%        		\label{fig:}
    	\end{subfigure}
}
\centering{
    	\begin{subfigure}[b]{0.3\textwidth}
        		\includegraphics[width=\textwidth]{CDC16_t200.png}
        		\caption{Map at $t=100$ sec}
%        		\label{fig:}
    	\end{subfigure}
	\hspace*{0.01\columnwidth}
	\begin{subfigure}[b]{0.3\textwidth}
        		\includegraphics[width=\textwidth]{CDC16_t250.png}
        		\caption{Map at $t=250$ sec}
%        		\label{fig:}
    	\end{subfigure}
	\hspace*{0.01\columnwidth}
	\begin{subfigure}[b]{0.3\textwidth}
        		\includegraphics[width=\textwidth]{CDC16_t300.png}
        		\caption{Map at $t=300$ sec}
%        		\label{fig:}
    	\end{subfigure}
}
\centering{
    	\begin{subfigure}[b]{0.3\textwidth}
        		\includegraphics[width=\textwidth]{CDC16_t350.png}
        		\caption{Map at $t=350$ sec}
%        		\label{fig:}
    	\end{subfigure}
	\hspace*{0.01\columnwidth}
	\begin{subfigure}[b]{0.3\textwidth}
        		\includegraphics[width=\textwidth]{CDC16_t400.png}
        		\caption{Map at $t=400$ sec}
%        		\label{fig:}
    	\end{subfigure}
	\hspace*{0.01\columnwidth}
	\begin{subfigure}[b]{0.3\textwidth}
        		\includegraphics[width=\textwidth]{CDC16_t450.png}
        		\caption{Map at $t=450$ sec}
%        		\label{fig:}
    	\end{subfigure}
}
	\caption{Autonomous Exploration of a 2D Space Using the Expanding Ring Approach}
	\medskip
	\small
	A robot (green circle, green marker of previous path) measures a room with a Kinect depth sensor to maximize map information gain.
\label{fig:AutonomousExploration}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.4\textwidth]{intel_clean.png}
	\caption{Intel Research Lab Floor Plan Benchmark~\cite{kummerle2009measuring}.}
	\medskip
	\small
	The 2D floor plan from the Intel Research Lab is simplified to eliminate small objects. The remaining black pixels are used to produce walls for 2D simulations.
\label{fig:intel}
\end{figure}

\begin{figure}[!ht]
    \centering
    \begin{subfigure}[t]{0.3\columnwidth}
        \centering
        \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{0min.png}
        \caption{$t=0$ min}
        \label{fig:IRL0min}
    \end{subfigure}
    \begin{subfigure}[t]{0.3\columnwidth}
        \centering
        \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{5min.png}
        \caption{$t=5$ min}
        \label{fig:IRL5min}
    \end{subfigure}
    \begin{subfigure}[t]{0.3\columnwidth}
           \centering
           \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{10min.png}
        \caption{$t=10$ min}
        \label{fig:IRL10min}
    \end{subfigure}
    \begin{subfigure}[t]{0.3\columnwidth}
           \centering
           \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{15min.png}
        \caption{$t=15$ min}
        \label{fig:IRL15min}
    \end{subfigure}
    \begin{subfigure}[t]{0.3\columnwidth}
         \centering
         \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{20min.png}
        \caption{$t=20$ min}
        \label{fig:IRL20min}
    \end{subfigure}
    \begin{subfigure}[t]{0.3\columnwidth}
           \centering
           \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{25min.png}
        \caption{$t=25$ min}
        \label{fig:IRL25min}
    \end{subfigure}
    \begin{subfigure}[t]{0.3\columnwidth}
           \centering
           \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{30min.png}
        \caption{$t=30$ min}
        \label{fig:IRL30min}
    \end{subfigure}
    \begin{subfigure}[t]{0.3\columnwidth}
           \centering
           \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{35min.png}
        \caption{$t=35$ min}
        \label{fig:IRL35min}
    \end{subfigure}
    \begin{subfigure}[t]{0.3\columnwidth}
           \centering
           \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{40min.png}
        \caption{$t=40$ min}
        \label{fig:IRL40min}
    \end{subfigure}
	\caption{Autonomous Exploration of the Intel Research Lab Using the Complete Cartesian Approach}
	\medskip
	\small
	A robot (green) measures a room in the ROS Stage simulator using the Intel Research Lab floor plan. The exact inverse sensor model is used for the autonomous exploration algorithm.
    \label{fig:IRL}
\end{figure}
